### 2021-04-19 README.Rmd
No EWN. Began generalizing the structure of the dynamics to allow for alternative functions for sampling. More to be done

* 2021-04-14 0.0.0.3200 Added NumNe to zoneDP output ready for its use in estimating FIS results by population and other numbers-at-size related indices. NumNe are the numbers-at-size following growth and the application of half of natural mortality but before any fishing mortality has occurred. (see News.ms for history of development)

@@

propD <- t(getzoneprops(zoneC,zoneDD,glb,year=47))
addtable(round(propD,4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[40:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last eight years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
plotconditioning(zoneDD,glb,zoneC,condC$histCE,1973:2019,rundir)
cmcda <- mcdahcr(arrce=condC$histCE,hsargs=hsargs,
                 yearnames=rownames(condC$histCE),saunames=glb$saunames,
                 acatches=tail(condC$histCatch,1))
pms <- cmcda$pms
multTAC <- cmcda$multTAC
out <- prepareprojectionnew(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            multTAC=multTAC,zoneDD=zoneDD,ctrl=ctrl,varyrs=7,
                            lastsigR = ctrl$withsigR)
zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP
zoneDDR <- out$zoneDDR

zoneDP <- doTASprojections(ctrl,zoneDP,zoneCP,condC$histCE,glb,mcdahcr,hsargs)
# save more plots to rundir ----------------------------------------------------
histCE <- condC$histCE
B0 <- getvar(zoneC,"B0")
ExB0 <- getvar(zoneC,"ExB0")
sauCI <- sauplots(zoneDP,zoneDDR,glb,rundir,B0,ExB0,startyr=25,addCI=TRUE,
                  histCE=histCE)
outzone <- poptozone(zoneDP,glb,
                     B0=sum(getvar(zoneC,"B0")),
                     ExB0=sum(getvar(zoneC,"ExB0")))
plotZone(outzone,rundir,CIprobs=c(0.05,0.5,0.95),addfile=TRUE)
projtime <- Sys.time()
print(projtime - starttime)
# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))

>>>>

* 2021-04-19 0.0.0.3000 Started development required to generalize the use of the doprojection function (it was previously called doTASprojection). This generalization requires the generation of separate functions to process the data for cpue, any FIS, and the numbers-at-size. Numerous diganostic plots have been added, also providing a template for adding more  (see News.md for history of development).

@@

propD <- t(getzoneprops(zoneC,zoneDD,glb,year=47))
addtable(round(propD,4),"propertyDD.csv",rundir,category="zoneDD",caption=
           "Properties of zoneD after conditioning on historical catches.")
addtable(round(t(zoneDD$harvestR[40:47,]),4),"final_harvestR.csv",rundir,
         category="zoneDD",caption="Last eight years of harvest rate.")
popdefs <- getlistvar(zone$zoneC,"popdef")
addtable(round(t(popdefs),3),"popdefs.csv",rundir,category="zoneDD",caption=
           "Population specific definitions")
# Prepare projections ----------------------------------------------------------
plotconditioning(zoneDD,glb,zoneC,condC$histCE,1973:2019,rundir)

indata <- list(arrce=condC$histCE,yearnames=rownames(condC$histCE),
               acatches=tail(condC$histCatch,1),fis=NA,nas=NA)
cmcda <- mcdahcr(indata,hsargs=hsargs,saunames=glb$saunames)
pms <- cmcda$pms
multTAC <- cmcda$multTAC
out <- prepareprojectionnew(projC=projC,condC=condC,zoneC=zoneC,glb=glb,
                            multTAC=multTAC,zoneDD=zoneDD,ctrl=ctrl,varyrs=7,
                            lastsigR = ctrl$withsigR)
zoneDP <- out$zoneDP
projC <- out$projC
zoneCP <- out$zoneCP
zoneDDR <- out$zoneDDR

zoneDP <- doprojections(ctrl,zoneDP,zoneCP,condC$histCE,glb,mcdahcr,hsargs,
                        tasCPUE,tasFIS,tasNaS)
# save more plots to rundir ----------------------------------------------------
histCE <- condC$histCE
B0 <- getvar(zoneC,"B0")
ExB0 <- getvar(zoneC,"ExB0")
sauout <- sauplots(zoneDP,zoneDDR,glb,rundir,B0,ExB0,startyr=25,addCI=TRUE,
                  histCE=histCE)
diagnosticsproj(sauout$zonePsau,glb,rundir,nrep=3)
outzone <- poptozone(zoneDP,glb,
                     B0=sum(getvar(zoneC,"B0")),
                     ExB0=sum(getvar(zoneC,"ExB0")))
plotZone(outzone,rundir,CIprobs=c(0.05,0.5,0.95),addfile=TRUE)
projtime <- Sys.time()
print(projtime - starttime)
# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(starttime),endtime=as.character(projtime))
